A Geometry for Network Visualization in \MakeLowercase{\texttt{ggplot2}}

### 2015-10-05 inst/paper.Rnw
all bot the protein example

\maketitle
\begin{abstract}
There are many implementations of static network visualization in R, but none are equipped with the flexibility and functionality of \texttt{ggplot2}.  \texttt{geom\_net} was created to fill this gap. Using two data frames to describe vertex and edge information, \texttt{geom\_net} makes use of the underlying structure of \texttt{ggplot2} to visualize networks. This makes it possible to easily facet networks according to covariates  or change aesthetics such as shape, size, or color according to additional edge or vertex information.
\end{abstract}
<<chunk_setup, echo=FALSE>>=
library(knitr)
opts_chunk$set(tidy = FALSE, echo=FALSE, cache=FALSE, eval = TRUE, message = FALSE, warning = FALSE,  fig.height = 8, fig.width = 8, fig.align = 'center',fig.show='hide')
@
<<readingdata, eval=TRUE, echo=FALSE>>=
library(ggplot2) # needs to be the version with geom_net!
 theme_net <- theme(aspect.ratio = 1, line = element_blank(), panel.background = element_blank(), plot.background = element_blank(), axis.text=element_blank(),axis.title=element_blank())
 data(blood, football, theme_elements, lesmis,madmen, mm_directed,email)
names(blood$vertices)[1] <- 'label'
#load("data/madmen.rda") # relative path should work for both of us
#load("data/mm_directed.rda")
#names(madmen$vertices)[1] <- 'label'
names(theme_elements$vertices)[1] <- 'label'
football$vertices$label <- as.factor(football$vertices$label)
football$vertices$value <- as.factor(football$vertices$value)
football$edges$in.conf <- 0
for (i in 1:nrow(football$edges)){
  idx1 <- which(football$vertices$label == football$edges$from[i])
  idx2 <- which(football$vertices$label == football$edges$to[i])
  if (football$vertices$value[idx1] == football$vertices$value[idx2]){
    football$edges$in.conf[i] <- 1
  }
}
#load("data/email.rda")
#email.net <- read.csv("data/email-data.csv")
#email.names <- data.frame(label = as.factor(unique(c(as.character(email.net$From),as.character(email.net$to)))))
#library(plyr)
#email.net <- ddply(email.net, .(eID), transform, nrecipients=length(to))
#employee <- read.csv("data/EmployeeRecords.csv")
#employee <- merge(email.names, employee, by.x="label", by.y="EmailAddress", all.x=T)
email.net <- email$edges
employee <- email$nodes
library(RColorBrewer)
cols <- brewer.pal(8, name="Set1")
load("data/protein.rda")

#yeast <- list(edges = protein, vertices = data.frame(label = min(yeast):max(yeast)))
yeast <- protein
@

\section{Introduction}
At its core, a network is simply a set of points connected in pairs by a set of lines \citep{newman}.  Here, we refer to the lines as edges and the points as vertices, although these are also called nodes.  These two seemingly simple sets of graphical objects, points and segments, are used to encode a huge variety and quantity of information across many fields of study. For instance, networks of scientific collaboration, a food web of marine animals, and American college football games are all covered in a paper on community detection in networks by \citet{football}.  Additionally, \citet{networkfailures} examine node failure in interdependent networks like power grids.  Social networks, such as links between actors found on \url{www.imdb.com}, and neural networks, like the completely mapped neural network of the \textit{C. elegans} worm are also etensively studied \citep{smallworld}.  Networks vary widely in scope and complexity: the smallest network is simply an edge between two vertices, while one of the most commonly used and most complex networks, the world wide web, has billions of vertices (webpages) and billions of edges (hyperlinks) connecting them.  The edges in a network can  be directed or undirected: directed edges represent information travelling from one vertex to another, and switching the direction would change the structure of the network. The world wide web is an example of a directed network because one webpage may link to another, and not necessarily the other way around. Undirected edges, however, are simply connections between vertices.  Coauthorship networks that encode information about academic publications are examples of undirected networks because if two people author a paper together, that creates a connection between them that is bidirectional.

@@

<<email_ex_facet, fig.height=8, fig.width=8, fig.cap = 'All emails within a company over a two week period facetted by day of the month.',echo=TRUE,eval=FALSE>>=
ggplot(data = subset(email.net, nrecipients < 54), aes(from_id = From, to_id = to)) +
  geom_net(vertices = employee, ealpha = 0.2, vsize = I(2), directed = TRUE,
           aes(vcolour=cols[as.numeric(CurrentEmploymentType)])) +
  expand_limits(x=c(0,1), y = c(0,1)) + facet_wrap(~day, nrow = 2) + theme_net
\begin{landscape}

@@

\includegraphics[width=8in]{figure/email_ex_facet-1.pdf}

@@

\end{landscape}

@@

ggplot(data = theme_elements$edges, aes(from_id = parent, to_id = child)) +
  geom_net(vertices = theme_elements$vertices, directed = TRUE, vlabel = TRUE) +
  expand_limits(x = c(0,1.2), y = c(0,1)) +
  theme_net

@@

The inheritance structure is plotted in figure \ref{fig.cap:theme_ex}.  In this plot, it is easy to quickly determine the parent and child vertices. Using this plot made creation of the \texttt{theme\_net} object used throughout these examples very simple. We just made set each of the major parent elements, \texttt{text}, \texttt{rect}, and \texttt{line} to \texttt{element\_blank()} and then set the aspect ratio equal to one.
  \subsection{Mad Men Networks}
  The following code creates the network example given in the introduction. We changed the vertex size and edge color for all vertices and edges, included vertex labels, and colored the vertices according to the character's gender.
<<print_ex, ref.label="madmen_ex", eval=FALSE, echo=TRUE,cache=FALSE>>=
@
 There is another Mad Men network included in the \texttt{gcookbook} package \citep{madmen}. It is a directed network, also of romantic relationships between characters, but it also includes advances made by one character that were rejected by the other.  For example, Roger Sterling made advances toward Betty Draper, but Betty refused him, and so there is a directed edge going from Roger to Betty, but not from Betty to Roger.  If the advance is reciprocated, like between Sal Romano and the Bellhop, there are two directed edges between the two vertices.
<<madmen2_ex,echo=TRUE, fig.cap= 'A directed network of relationships in Mad Men.'>>=
ggplot(data = mm.directed$edges, aes(from_id = Name1, to_id = Name2)) +
  geom_net(vertices = mm.directed$vertices, directed = T, vlabel = T,
           vsize = I(2.5), layout = 'fruchtermanreingold',
           aes(vcolour=c( "#FF69B4", "#0099ff")[as.numeric(Gender)])) +
  expand_limits(x = c(0,1.1), y = c(0,1)) + theme_net
@
\begin{figure}
\centering
\includegraphics[width=\textwidth]{figure/madmen2_ex-1.pdf}
\caption{\label{fig.cap:madmen2_ex} A directed network of relationships in Mad Men.}
\end{figure}
This network is shown in figure \ref{fig.cap:madmen2_ex}.  This network is much more connected than the previous Mad Men example.  It also allows us to see much more of the drama in the show. For instance, you can see that Roger made advances towards Betty, his business partner's wife, which is much more scandalous than what we can see in the first network.

  \subsection{College Football}
  This next example comes from M.E.J. Newman's network data web page \citep{football}.  It is an undirected network consisting of all regular season college football games played between Division I schools in Fall of 2000.  There are 115 vertices and 613 edges: each vertex represents a school, and an edge represents a game played between two schools. There is an additional variable in the vertex data frame corresponding to the conference each team belongs to, and there is an additional variable in the edge data frame that is equal to one if the game occured between teams in the same conference or zero if the game occured between teams in different conferences.
<<football_ex, echo=TRUE, fig.cap="All regular season Division I college football games in the Fall 2000 season.">>=
colors <- brewer.pal(12, name = 'Paired')
ggplot(data = football$edges, aes(from_id = from, to_id = to,
                                  elinetype = in.conf + 1)) +
  geom_net(vertices = football$vertices, ealpha = 0.3, vsize = 2, vlabel = TRUE,
           aes(vcolour=colors[as.numeric(factor(value))])) +
  expand_limits(x = c(0,1), y = c(0,1)) + theme_net
@
The network of football games is given in figure \ref{fig.cap:football_ex}. Here, we have changed the \texttt{elinetype} aesthetic to correspond to games that occur between teams in the same conference or different conferences.  These lines are dotted and solid, respectively. We have also assigned a different color to each conference, and the vertices and their labels are colored according to their conference. This coloring and changing of the linetypes make the structure of the game network easier to view.  There is one conference consisting of Navy, Notre Dame, Utah State, Central Florida, and Connecticut, which is spread out all over the network, whereas most other conferences' teams are all very close to each other because they play within conference much more than they play out of conference.  At the time, these five schools were all independents and did not have a home conference.  Without the coloring capability, we would not have been able to pick out that difference as easily.
\begin{figure}
\centering
\includegraphics[width=\textwidth]{figure/football_ex-1.pdf}
\caption{\label{fig.cap:football_ex} The network of regular season Division I college football games in the season of fall 2000. The vertices and their labels are colored by conference.}
\end{figure}
\afterpage{\clearpage}

  \subsection{Les Mis\'{e}rables}
  This next network comes from \citet{lesmis}. It is an undirected network of coappearances of characters in Victor Hugo's \emph{Les Mis\'{e}rables}.  There are 77 vertices representing each of the 77 characters in the book, and an edge connects two vertices if those two characters appear in the same chapter of the book.  There are 254 edges in this network. The edges are also weighted by the number of coappearances. The largest weighting is 31, between the characters Jean Valjean and Cosette.  This network is shown in figure \ref{fig.cap:lesmis_ex}. This network reveals many important character groups, as well as the main characters in the story.  The main characters are the ones with high degree, like Valjean, Cosette, and Javert.  There is an extremely wide edge connecting Valjean and Cosette, which implies that they are strongly connected; in fact, Cosette is Valjean's adopted daughter.
<<lesmis_ex, echo=TRUE, fig.cap="Coappearance network of characters in Victor Hugo's \\emph{Les Mis\\'{e}rables}">>=
ggplot(data = lesmis$edges, aes(from_id = from, to_id = to,
                                esize = value/mean(value))) +
  geom_net(vertices = lesmis$vertices, ealpha = 7/10,
           vcolour = I("red"), vsize = I(2.5),
           layout = 'fruchtermanreingold', vlabel=TRUE) +
  expand_limits(x = c(0,1.1), y = c(0,1)) + theme_net
@
\begin{figure}
\centering
\includegraphics[width=\textwidth]{figure/lesmis_ex-1.pdf}
\caption{\label{fig.cap:lesmis_ex} Co-appearance network of characters in Victor Hugo's \emph{Les Mis\'{e}rables}.}
\end{figure}
\afterpage{\clearpage}

  \subsection{Protein Interaction Network in Yeast}
  This example of a protein interaction network comes from \citet{protein}. It is the complete protein-protein interaction network in the yeast species \emph{S. cerevisiae}. There are 1,870 proteins that make up the vertices of this network, and there are 2,240 edges between them.  These edges represent ``direct physical interactions" between any 2 proteins \citep[][p. 42]{protein}. Because the network is very large, we randomly sampled 500 interactions and their associated proteins to plot it in figure \ref{fig.cap:yeast_ex}.  We also demonstrate the layout capabilities by changing the layout to random and setting the distribution to \texttt{"uniang"}, which is a  ``gaussian donut" layout.  Indeed, we see a nearly round area in the middle of the graph where the layout parameter has forced there to be no vertices.

<<yeast_code>>=
sample.edges <- yeast$edges[sample(nrow(yeast$edges), 500),]
yeast.samp <- list(edges = sample.edges, vertices = data.frame(label = unique(c(sample.edges$V1,sample.edges$V2))))
@
<<yeast_ex, echo=TRUE, fig.cap="Protein in protein interation network in yeast.", cache=FALSE>>=
ggplot(data = yeast.samp$edges, aes(from_id = V1, to_id = V2)) +
  geom_net(vertices = yeast.samp$vertices, ealpha = .25, valpha = .5,
           vcolour = 'magenta', layout = 'random',
           layout.par = list(dist = 'uniang')) +
  expand_limits(x = c(0,1), y = c(0,1)) + theme_net
@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figure/yeast_ex-1.pdf}
\caption{\label{fig.cap:yeast_ex} A subset of the complete protein-protein interaction network in \emph{S. cerevisiae}. The layout is random.}
\end{figure}
\afterpage{\clearpage}

\section{Technical Details}

>>>>

\maketitle
\begin{abstract}
There are many implementations of static network visualization in R, but none are equipped with the flexibility and functionality of \texttt{ggplot2}.  \texttt{geom\_net} was created to fill this gap. Using two data frames to describe vertex and edge information, \texttt{geom\_net} makes use of the underlying structure of \texttt{ggplot2} to visualize networks. This makes it possible to easily facet networks according to covariates  or change aesthetics such as shape, size, or color according to additional edge or vertex information.
\end{abstract}
<<chunk_setup, echo=FALSE>>=
library(knitr)
opts_chunk$set(tidy = FALSE, echo=FALSE, cache=FALSE, eval = TRUE, message = FALSE, warning = FALSE,  fig.height = 8, fig.width = 8, fig.align = 'center',fig.show='hide')
@
<<readingdata, eval=TRUE, echo=FALSE>>=
library(ggplot2) # needs to be version ≥ 1.0.1.9003
library(ggnet) # install from github
data(blood, football, theme_elements, lesmis,madmen, mm_directed, email)

data(protein)
library(RColorBrewer)
cols <- brewer.pal(8, name="Set1")
yeast <- protein

# set up networks for all of the data sets
MMnet <- merge(madmen$edges, madmen$vertices, by.x="Name1", by.y="label", all=TRUE)
MM2net <- merge(mm.directed$edges, mm.directed$vertices, by.x="Name1", by.y="label", all=TRUE)
bloodnet <- merge(blood$edges, blood$vertices, by.x="from", by.y="label", all=TRUE)

employee <- data.frame(expand.grid(
              label=unique(email$nodes$label), day=unique(email$edges$day)))
employee <- merge(employee, email$nodes, by="label")
emailnet <- merge(subset(email$edges, nrecipients < 54), employee, by.x=c("From", "day"), by.y=c("label", "day"), all=TRUE)

TEnet <- merge(theme_elements$edges, theme_elements$vertices, by.x="parent", by.y="name", all=TRUE)

football$edges$in.conf <- 1
for (i in 1:nrow(football$edges)){
  idx1 <- which(football$vertices$label == football$edges$from[i])
  idx2 <- which(football$vertices$label == football$edges$to[i])
  if (football$vertices$value[idx1] == football$vertices$value[idx2]){
    football$edges$in.conf[i] <- 0
  }
}
ftnet <- merge(football$edges, football$vertices, by.x="from", by.y="label", all=TRUE)

\hh{todo list:
\begin{enumerate}
\item there is no protein.rda in the data folder - could you please put it there?
\item include installation instruction for package ggnet
\end{enumerate}
}
\section{Introduction}
At its core, a network is simply a set of points connected in pairs by a set of lines \citep{newman}.  Here, we refer to the lines as edges and the points as vertices, although these are also called nodes.  These two seemingly simple sets of graphical objects, points and segments, are used to encode a huge variety and quantity of information across many fields of study. For instance, networks of scientific collaboration, a food web of marine animals, and American college football games are all covered in a paper on community detection in networks by \citet{football}.  Additionally, \citet{networkfailures} examine node failure in interdependent networks like power grids.  Social networks, such as links between actors found on \url{www.imdb.com}, and neural networks, like the completely mapped neural network of the \textit{C. elegans} worm are also etensively studied \citep{smallworld}.  Networks vary widely in scope and complexity: the smallest network is simply an edge between two vertices, while one of the most commonly used and most complex networks, the world wide web, has billions of vertices (webpages) and billions of edges (hyperlinks) connecting them.  The edges in a network can  be directed or undirected: directed edges represent information travelling from one vertex to another, and switching the direction would change the structure of the network. The world wide web is an example of a directed network because one webpage may link to another, and not necessarily the other way around. Undirected edges, however, are simply connections between vertices.  Coauthorship networks that encode information about academic publications are examples of undirected networks because if two people author a paper together, that creates a connection between them that is bidirectional.

@@

%\begin{landscape}

@@

<<email_ex_facet, fig.height=5, fig.width=8, fig.cap = 'All emails within a company over a two week period facetted by day of the month.',echo=TRUE, out.width='\\textwidth'>>=
ggplot(data = emailnet, aes(from_id = From, to_id = to)) +
  geom_net(aes(colour= CurrentEmploymentType), fiteach=TRUE,
           linewidth=0.5, alpha=0.2, size=2) +
  scale_colour_brewer(palette="Set1") + theme_net() +
  theme(legend.position="bottom") + facet_wrap(~day, nrow = 2)
\includegraphics[width=\textwidth]{figure/email_ex_facet-1.pdf}

@@

%\end{landscape}

@@

ggplot(data = TEnet, aes(from_id = parent, to_id = child)) +
  geom_net(directed = TRUE, label = TRUE, vjust=-.5) +
  theme_net() + xlim(c(-0.05, 1.05))

@@

The inheritance structure is plotted in figure \ref{fig.cap:theme_ex}.  In this plot, it is easy to quickly determine the parent and child vertices. Using this plot made creation of the \texttt{theme\_net} object used throughout these examples very simple. We just made set each of the major parent elements, \texttt{text}, \texttt{rect}, and \texttt{line} to \texttt{element\_blank()} and then set the aspect ratio equal to one.
  \subsection{Mad Men Networks}
  The following code creates the network example given in the introduction. We changed the vertex size and edge color for all vertices and edges, included vertex labels, and colored the vertices according to the character's gender.
<<print_ex, ref.label="madmen_ex", eval=FALSE, echo=TRUE,cache=FALSE>>=
@
 There is another Mad Men network included in the \texttt{gcookbook} package \citep{madmen}. It is a directed network, also of romantic relationships between characters, but it also includes advances made by one character that were rejected by the other.  For example, Roger Sterling made advances toward Betty Draper, but Betty refused him, and so there is a directed edge going from Roger to Betty, but not from Betty to Roger.  If the advance is reciprocated, like between Sal Romano and the Bellhop, there are two directed edges between the two vertices.
<<madmen2_ex,echo=TRUE, fig.cap= 'A directed network of relationships in Mad Men.'>>=
ggplot(data = MM2net, aes(from_id = Name1, to_id = Name2)) +
  geom_net(aes(colour=Gender), directed=TRUE, label=TRUE,
           size=2.5, layout='fruchtermanreingold') +
  scale_colour_manual(values=c( "#FF69B4", "#0099ff")) +
  theme_net() + xlim(c(-.1, 1.1)) + theme(legend.position="bottom")
@
\begin{figure}
\centering
\includegraphics[width=\textwidth]{figure/madmen2_ex-1.pdf}
\caption{\label{fig.cap:madmen2_ex} A directed network of relationships in Mad Men.}
\end{figure}
This network is shown in figure \ref{fig.cap:madmen2_ex}.  This network is much more connected than the previous Mad Men example.  It also allows us to see much more of the drama in the show. For instance, you can see that Roger made advances towards Betty, his business partner's wife, which is much more scandalous than what we can see in the first network.

  \subsection{College Football}
  This next example comes from M.E.J. Newman's network data web page \citep{football}.  It is an undirected network consisting of all regular season college football games played between Division I schools in Fall of 2000.  There are 115 vertices and 613 edges: each vertex represents a school, and an edge represents a game played between two schools. There is an additional variable in the vertex data frame corresponding to the conference each team belongs to, and there is an additional variable in the edge data frame that is equal to one if the game occured between teams in the same conference or zero if the game occured between teams in different conferences.
<<football_ex, echo=TRUE, fig.cap="All regular season Division I college football games in the Fall 2000 season.">>=
sid <- which(ftnet$from %in% c("Navy", "NotreDame", "UtahState", "CentralFlorida", "Connecticut"))
ftnet$schools <- ""
ftnet$schools[sid] <- ftnet$from[sid]

ggplot(data=ftnet, aes(from_id=from, to_id=to)) +
  geom_net(aes(colour=value, linewidth=(2-in.conf)/3,  label=schools),
           size=4, ecolour="grey30", vjust=-0.5,
           alpha=0.3, layout='fruchtermanreingold') +
  scale_colour_brewer("Conference", palette="Paired") + theme_net() +
  theme(legend.position="bottom") + xlim(c(-0.05, 1.05))
@
The network of football games is given in figure \ref{fig.cap:football_ex}. Here, we have changed the \texttt{elinetype} aesthetic to correspond to games that occur between teams in the same conference or different conferences.  These lines are dotted and solid, respectively. We have also assigned a different color to each conference, and the vertices and their labels are colored according to their conference. This coloring and changing of the linetypes make the structure of the game network easier to view.  There is one conference consisting of Navy, Notre Dame, Utah State, Central Florida, and Connecticut, which is spread out all over the network, whereas most other conferences' teams are all very close to each other because they play within conference much more than they play out of conference.  At the time, these five schools were all independents and did not have a home conference.  Without the coloring capability, we would not have been able to pick out that difference as easily.
\begin{figure}
\centering
\includegraphics[width=\textwidth]{figure/football_ex-1.pdf}
\caption{\label{fig.cap:football_ex} The network of regular season Division I college football games in the season of fall 2000. The vertices and their labels are colored by conference.}
\end{figure}
\afterpage{\clearpage}

  \subsection{Les Mis\'{e}rables}
  This next network comes from \citet{lesmis}. It is an undirected network of coappearances of characters in Victor Hugo's \emph{Les Mis\'{e}rables}.  There are 77 vertices representing each of the 77 characters in the book, and an edge connects two vertices if those two characters appear in the same chapter of the book.  There are 254 edges in this network. The edges are also weighted by the number of coappearances. The largest weighting is 31, between the characters Jean Valjean and Cosette.  This network is shown in figure \ref{fig.cap:lesmis_ex}. This network reveals many important character groups, as well as the main characters in the story.  The main characters are the ones with high degree, like Valjean, Cosette, and Javert.  There is an extremely wide edge connecting Valjean and Cosette, which implies that they are strongly connected; in fact, Cosette is Valjean's adopted daughter.
<<lesmis_ex, echo=TRUE, fig.cap="Coappearance network of characters in Victor Hugo's \\emph{Les Mis\\'{e}rables}">>=
lesmisnet <- merge(lesmis$edges, lesmis$vertices, by.x="from", by.y="label", all=TRUE)

ggplot(data = lesmisnet, aes(from_id = from, to_id = to, linewidth = value/5)) +
  geom_net(alpha = 7/10, colour = "red", size = 2.5,
           layout = 'fruchtermanreingold', label=TRUE) +
  theme_net()
@
\begin{figure}
\centering
\includegraphics[width=\textwidth]{figure/lesmis_ex-1.pdf}
\caption{\label{fig.cap:lesmis_ex} Co-appearance network of characters in Victor Hugo's \emph{Les Mis\'{e}rables}.}
\end{figure}
\afterpage{\clearpage}

%'   \subsection{Protein Interaction Network in Yeast}
%'   This example of a protein interaction network comes from \citet{protein}. It is the complete protein-protein interaction network in the yeast species \emph{S. cerevisiae}. There are 1,870 proteins that make up the vertices of this network, and there are 2,240 edges between them.  These edges represent ``direct physical interactions" between any 2 proteins \citep[][p. 42]{protein}. Because the network is very large, we randomly sampled 500 interactions and their associated proteins to plot it in figure \ref{fig.cap:yeast_ex}.  We also demonstrate the layout capabilities by changing the layout to random and setting the distribution to \texttt{"uniang"}, which is a  ``gaussian donut" layout.  Indeed, we see a nearly round area in the middle of the graph where the layout parameter has forced there to be no vertices.
%'
%' <<yeast_code>>=
%' sample.edges <- yeast$edges[sample(nrow(yeast$edges), 500),]
%' yeast.samp <- list(edges = sample.edges, vertices = data.frame(label = unique(c(sample.edges$V1,sample.edges$V2))))
%' @
%' <<yeast_ex, echo=TRUE, fig.cap="Protein in protein interation network in yeast.", cache=FALSE>>=
%' ggplot(data = yeast.samp$edges, aes(from_id = V1, to_id = V2)) +
%'   geom_net(vertices = yeast.samp$vertices, ealpha = .25, valpha = .5,
%'            vcolour = 'magenta', layout = 'random',
%'            layout.par = list(dist = 'uniang')) +
%'   expand_limits(x = c(0,1), y = c(0,1)) + theme_net
%' @
%'
%' \begin{figure}
%' \centering
%' \includegraphics[width=\textwidth]{figure/yeast_ex-1.pdf}
%' \caption{\label{fig.cap:yeast_ex} A subset of the complete protein-protein interaction network in \emph{S. cerevisiae}. The layout is random.}
%' \end{figure}
%' \afterpage{\clearpage}
%'
%'
\section{Technical Details}
